Efficient Coalition Formation \\ for Web Services

### 2013-06-11 papers/coalition-journal-extension/coalition_journal.tex
Changes

The communities and web services earn revenue by performing tasks. The total gain is function of quality ($QoS_{ws}$) and quantity($Tr_{ws}$) of tasks being performed. As mentioned in section \ref{ws_parameters} $QoS_{ws}$ is obtained by a certain aggregation function of the parameters considered in Table \ref{qosws}. We have adopted a linear equal weigth average over all QoS parameteres listed in table \ref{qosws} excluding the $Throuput$ and $Cost$ parameters. A community has the option to weigh specific QoS patameters more or less depending on the expectations of their clients.

@@

Now we consider another example, in which we have different comunitites with different market share and ${R_C}$ values, and also web services having a small share of market share independantly, providing them with a small task pull. In these kind of scenarios, the solution considers individual maximization of payoff and also the total worth of all communities which represents the $social welfare$. In this example the most efficient partition of web services is earned by having two coalitions of $\left\{C_1, ws_2\right\}$ and $\left\{C_2, ws_1, ws_3\right\}$, which yeilds a total value of $32 + 16 = 48$. In these type of scenarios,

>>>>

The communities and web services earn revenue by performing tasks. The total gain is function of quality ($QoS_{ws}$) and quantity($Tr_{ws}$) of tasks being performed. As mentioned in section \ref{ws_parameters}, $QoS_{ws}$ is obtained by a certain aggregation function of the parameters considered in Table \ref{qosws}. We have adopted a linear equal weigth average over all QoS parameteres listed in table \ref{qosws} excluding the $Throuput$ and $Cost$ parameters. A community has the option to weigh specific QoS patameters more or less depending on the expectations of their clients.

@@

Now we consider another example, in which we have different comunitites with different market share, ${R_C}$ values. Web services also have a small share of market independantly, providing them with a small task pull. In these kind of scenarios, the solution considers individual maximization of payoff and also the total worth of all communities which represents the $social welfare$. In this example the most efficient partition of web services is earned by having two coalitions of $\left\{C_1, ws_2\right\}$ and $\left\{C_2, ws_1, ws_3\right\}$, which yeilds a total value of $32 + 16 = 48$. In these type of scenarios, the goal is to reach stability, adopting a distributed approach where all players have the power of choice on the decision of whether or not they join a coalition. The communities usually start the game having some stablished members, encountring new web services, the communities may exchange web services and new web services would join them having at least one player gaining utility, without hurting any other participant. In this example if we initially having two coalitions of $\left\{C_1, ws_2\right\}$ and $\left\{C_2, ws_1\right\}$ and a ${ws_3}$ as new webservice, ${ws_3}$ joining ${C_1}$ would hurt at least itself or $ws_2$, however ${ws_3}$ joining ${C_2}$ would not hurt any participants and ${ws_3}$ would earn more within the community and the community will have enough web services performing the incoming tasks from users.
